---
title: "GenderClassifier"
author: "HilaReut"
date: "April 25, 2016"
output: html_document
---

Gender classifier data:
This data set was used to train a CrowdFlower AI gender predictor.
Contributors were asked to simply view a Twitter profile and judge whether the user was a male, a female, or a brand (non-individual). The dataset contains 20,000 rows, each with a user name, a random tweet, account profile and image, location, and even link and sidebar color.

We choose to analyze what are the uses words by male and by female. and to see if we can learn about male and female tweets. 

Downloaded the data from : http://www.crowdflower.com/data-for-everyone/

```{r }
library(RCurl)
#Get the data
url = "http://www.crowdflower.com/wp-content/uploads/2016/03/gender-classifier-DFE-791531.csv"
file = getURL(url)
data = read.csv(text = file)
```

Arrange the data - because we have a big dataset with 20,000 rows, we needed to arrange the data .  we took 3,000 rows.

```{r}
#Manipulate the data 
data <- data[data$X_unit_id < 815720437,] 

```

We wanted to test whether there is a difference in amount of female use Twitter, compared with the amount of male uses Tweitter.

```{r}
#Get female - male relation
length(data$gender=="male")
length(data$gender=="female")

```

We saw that the amount is equal between boys and girls.
```{r}
#Display with barplot graph
a = c(length(data$gender=="male"),length(data$gender=="female"))
barplot(a,names.arg = c("male","female"),col = c("blue","red"), main="Amount of male and female use Twitter")


```

In order to find out what are the most frequent used words by males and females, on Twitter we had to take the following steps:
1. Take male/female text on twiteer .

```{r}
#Get all male twitter text
text_male = subset(data, data$gender=="male")
text_male = text_male$text
```

2.Create list of words from text_male
```{r}
#create list from text_male
text_male_list <- text_male[1:length(text_male)]
words = list()
for ( i in text_male_list) {
  # Merge the two lists.
  words <- c(words,unlist(strsplit(i," ")))
}

```
3.Create a list of word - frequency 
```{r}
#key = word , value = frequency
count = 0;
mylist = list()
for (word in words){
  for (xWord in words){
    if (word == xWord)
      count =  count + 1;
  }
  key <- word
  value <- count
  mylist[[ key ]] <- value
  count = 0;
}


```

4.Sort in descending order
```{r}
library(data.table)
#sort the data
DT1 = mylist
DT1 = data.table(x=c(names(mylist)),v=c(do.call(rbind, lapply(DT1, as.numeric))))
DT1 = DT1[order(-DT1$v),]

```

We chose 6 randomly words and display it with pie
```{r}
words_male = DT1[1:1200]
w1 = words_male[110]
w2 = words_male[164]
w3 = words_male[701]
w4 = words_male[272]
w5 = words_male[107]
w6 = words_male[1200]
# Simple Pie Chart
slices <- c(w1$v,w2$v,w3$v,w4$v,w5$v,w6$v)
lbls <- c(w1$x,w2$x,w3$x,w4$x,w5$x,w6$x)
pie(slices, labels = lbls, main="Pie Chart Males frequency words")
```

A few words's explantion we found:
@onedirection is a boy band
#AMAs  is a tag for American Music Awards
#SPECTRE is james bond film

We did the same for females

```{r}
#Get all female twitter text
text_female = subset(data, data$gender=="female")
text_female = text_female$text
print(length(text_female))
v <- text_female[1:length(text_female)]
#create list of key and value 
#key = word , value = frequency
x = list()
for ( i in v) {
  # Merge the two lists.
  x <- c(x,unlist(strsplit(i," ")))
}
count = 0;
mylist = list()
for (word in x){
  for (xWord in x){
    if (word == xWord)
      count =  count + 1;
  }
  key <- word
  value <- count
  mylist[[ key ]] <- value
  count = 0;
}
#sort the data
DT = mylist
DT = data.table(x=c(names(mylist)),v=c(do.call(rbind, lapply(DT, as.numeric))))
DT = DT[order(-DT$v),]
#create plot
words_female = DT[1:1200]
wf1 = words_female[110]
wf2 = words_female[107]
wf3 = words_female[345]
wf4 = words_female[272]
wf5 = words_female[618]
wf6 = words_female[1200]


# Simple Pie Chart
slices <- c(wf1$v,wf2$v,wf3$v,w4$v,wf5$v,wf6$v)
lbls <- c(wf1$x,wf2$x,wf3$x,wf4$x,wf5$x,wf6$x)
pie(slices, labels = lbls, main="Pie Chart of females frequency words")

```


We can see from randomly 6 words that girls tend to be more emoitinal due to tags they use.  

To sum up, of course, isn???t to say that every female account we saw had one of those, but rather that if a heart or for example the above words appeared in a tweet or profile, the model was very confident that account belonged to a woman.