---
title: "Grey's Anatomy"
author: "HIlaReut"
date: "16 May 2016"
output: html_document
---

```{r}
library(igraph)
require(igraph)

```

Grey's anatomy data

```{r}
edges.data = read.csv('ga_edgelist.csv',header = T)
ga_edges =  graph.data.frame(edges.data,directed = F)
summary(ga_edges)
V(ga_edges)$name
#Remove self-Loops is exist 
ga_edges = simplify(ga_edges)
```

Calculate Betweenness
```{r}
#Calculate betweenness 
ga_bet = betweenness(ga_edges)
ga_bet = sort(ga_bet,decreasing = T)
names(ga_bet[1])

```

Calculate closeness
```{r}
#Calculate closeness 
ga_close = closeness(ga_edges)
ga_close = sort(ga_close, decreasing = T)
names(ga_close[1])
```

Calculate eigenvector
```{r}
#Calculate eigenvector
ga_eigen = evcent(ga_edges)
ga_eigen = sort(ga_eigen$vector, decreasing = T)
names(ga_eigen[1])

```

<h5>Find commuinty with Girvan-Newman community detection. </h5>

```{r}
fc = edge.betweenness.community(ga_edges)

```

Cheack what is the modularity

```{r}
#Cheack what is the modularity
fc$modularity

#What partition is the best?
max(fc$modularity)
which.max(fc$modularity)

#Color nodes by partitions 
memb = membership(fc)
plot(ga_edges, vertex.size=7, vertex.label=NA,
     vertex.color=memb, asp=FALSE)

#How many communities received
max(levels(as.factor(memb)))

#What size of each commuinty
summary(as.factor(memb))
```

<h5>Find commuinty with Multi-Level algorithm. </h5> <br>
This function implements the multi-level modularity optimization algorithm for finding community structure.
```{r}

ml = multilevel.community(ga_edges)

#Cheack what is the modularity
ml$modularity

#What partition is the best?
max(ml$modularity)
which.max(ml$modularity)

#Color nodes by partitions 
memb = membership(ml)
plot(ga_edges, vertex.size=7, vertex.label=NA,
     vertex.color=memb, asp=FALSE)

#How many communities received
max(levels(as.factor(memb)))

#What size of each commuinty
summary(as.factor(memb))

```

<h5>Find commuinty with propagating labels algorithm </h5>
This is a fast, nearly linear time algorithm for detecting community structure in networks.
In works by labeling the vertices with unique labels and then updating the labels by majority voting in the neighborhood of the vertex.
```{r}

#Find commuinty with propagating labels algorithm
#This is a fast, nearly linear time algorithm for detecting community structure in networks.
#In works by labeling the vertices with unique labels and then updating the labels by majority voting in the neighborhood of the vertex.
pl = label.propagation.community(ga_edges)

#Cheack what is the modularity
pl$modularity

#What partition is the best?
max(pl$modularity)
which.max(pl$modularity)

#Color nodes by partitions 
memb = membership(pl)

plot(ga_edges, vertex.size=8, vertex.label=NA,
     vertex.color=memb, asp=FALSE)

#How many communities received
max(levels(as.factor(memb)))

#What size of each commuinty
summary(as.factor(memb))



```

